The Hyperedge Event Model

### 2018-11-01 paper/revision1/ba-sample.tex
adding SBM

The models discussed above are those, like HEM,  in which edge formation is driven by subgraph structure. There is another class of network models, originating with the latent space model introduced by \cite{hoff2002}, in which tie formation is modeled by embedding nodes in a space of latent attributes. Under this modeling framework, each node is attributed with a coordinate in a metric space, and the likelihood of a tie between two nodes is inversely related to the distance between the two nodes in the metric space. The latent space model has seen several extensions, the latest of which tis the latent factor model proposed by \cite{minhas2016inferential}. A number of dynamic extensions of the latent space framework have been developed \citep[e.g., ][]{sarkar2005dynamic,sewell2015latent,ward2013gravity}. The HEM, as we have presented it, does not involve latent node attributes, but in future work the HEM could be extended to incorporate latent node features---resulting in a latent space model for dynamic hyperedges.

>>>>

The models discussed above are those, like HEM,  in which edge formation is driven by subgraph structure. There is another class of network models, originating with the latent space model introduced by \cite{hoff2002}, in which tie formation is modeled by embedding nodes in a space of latent attributes. Under this modeling framework, each node is attributed with a coordinate in a metric space, and the likelihood of a tie between two nodes is inversely related to the distance between the two nodes in the metric space. The latent space model has seen several extensions, the latest of which tis the latent factor model proposed by \cite{minhas2016inferential}. A number of dynamic extensions of the latent space framework have been developed \citep[e.g., ][]{sarkar2005dynamic,sewell2015latent,ward2013gravity}. Another popular form of latent variable model for networks is the stochastic block model (SBM) \citep{holland1983stochastic,airoldi2008mixed}. In the SBM, each vertex is associated with one or more blocks, and each block is attributed with a vector of parameters that determines the rate at which members of the respective block form ties with members of each block. The blocks reduce vertex-to-vertex tie probabilities to block-to-block tie probabilities. Like the latent space model, the SBM has been extended to model discrete-time longitudinal networks  \citep{matias2017statistical}. The HEM, as we have presented it, does not involve latent node attributes, but in future work the HEM could be extended to incorporate latent node features---resulting in a latent space model and/or SBM for dynamic hyperedges.
